### 2011-12-04 paper_draft.tex
added some keywords for the first paragraph of the discussion

>>>>

Plot: Maybe plot the amount of new added datasets and the number of new phenotypes per

Paragraph 1:

First focus on biological issues:

Polymorphisms to phenotypes, correlation only.
Bias in the samples collected by openSNP?
Sample size to small?
Quality check for phenotypes?
Mapping to haplotype blocks?
Combination with the hapmap
Manage increasing amount of data?

Paragraph 2:
from great power follows great responsibility!

Imagine a world where all data is free...
What privacy issues do arise? 
Is there an effective mechanism to avoid abuse or
genetic discrimination?
How should governments treat the additional  data?
